---
title: "Working with sf objects"
author: "Sofie Thinggaard"
date: "22-02-08 updated `r Sys.Date()`"
output:
  html_document: default
---

## Installing packages
```{r}
#install.packages("raster")
library(raster)
#install.packages("sf")
library(sf)
#install.packages("tmap")
library(tmap)
#install.packages("spData")
library(spData)

# To install the spDataLarge uncomment the next line
#install.packages("spDataLarge", repos = "https://geocompr.r-universe.dev")
library(spDataLarge)
```


#  Exercise 1 - Make a map

## Non-improved map
```{r initial-map}
tm_shape(nz_elev)  +
  tm_raster(title = "elev", 
            style = "cont",
            palette = "BuGn") +
  tm_shape(nz) +
  tm_borders(col = "red", 
             lwd = 3) +
  tm_scale_bar(breaks = c(0, 100, 200),
               text.size = 1) +
  tm_compass(position = c("LEFT", "center"),
             type = "rose", 
             size = 2) +
  tm_credits(text = "A. Sobotkova, 2022") +
  tm_layout(main.title = "My map",
            bg.color = "orange",
            inner.margins = c(0, 0, 0, 0))
```


# Tasks 

1. Change the map title from "My map" to "New Zealand".
2. Update the map credits with your own name and today's date.
3. Change the color palette to "-RdYlGn". 
  (You can also try other palettes from http://colorbrewer2.org/)
4. Put the north arrow in the top right corner of the map.
5. Improve the legend title by adding the used units (m asl).
6. Increase the number of breaks in the scale bar.
7. Change the borders' color of the New Zealand's regions to black. 
  Decrease the line width.
8. Change the background color to any color of your choice.


## Your solution
```{r improved-map}
tm_shape(nz_elev)  +
  tm_raster(title = "m asl", 
            style = "cont",
            palette = "-RdYlGn") +
  tm_shape(nz) +
  tm_borders(col = "black", 
             lwd = 1) +
  tm_scale_bar(breaks = c(0, 50, 100, 150, 200),
               text.size = 1) +
  tm_compass(position = c("RIGHT", "top"),
             type = "rose", 
             size = 2) +
  tm_credits(text = "S. Thinggaard, 08-February-2022") +
  tm_layout(main.title = "New Zealand",
            bg.color = "pink",
            inner.margins = c(0, 0, 0, 0))
```

# Exercise 2 - Inspect and display spatial data

####  Preparation: Load data from provided package
```{r load-data}
#install.packages("rgdal") #need additional package to work
library(rgdal)

srtm  <-  raster(system.file("raster/srtm.tif", package = "spDataLarge"))
zion  <-  read_sf(system.file("vector/zion.gpkg", package = "spDataLarge"))
```

## Instructions and questions

```{r}
zion
```

* Display the `zion` object and view its structure.
  - What can you say about the content of this file?
Latitude (Y), longitude (X) coordinates of things like mountains, lakes, anything with a unit code/name in Zion national park.
1 observation and 12 variables

  - What type of data does it store? 
Spatial data: information about geographic
location. More specifically vector information.

  - What is the coordinate system used?
CRS= +proj=utm
```{r}
crs(zion)
```

  
  - How many attributes does it contain?
```{r}
attributes(zion)
```


  - What is its geometry?
Polygon

* Display the `srtm` object and view its structure.
```{r}
srtm
```

  - What can you say about the content of this file? 
Dataset with polygons representing borders of the National Park.

  - What type of data does it store?
Spatial data: raster information.

  - What is the coordinate system used?
CRS= +proj=longlat
```{r}
crs(srtm)
```


  - How many attributes does it contain?
```{r}
attributes(srtm)
```

  
  - How many dimensions does it have?
Nrows= 457
Ncols= 465
Ncell= 212505
  
  - What is the data resolution?
0.0008333333, 0.0008333333  (x, y) 

# Exercise 3 - Reconciling Coordinate systems

## Instructions

* Reproject the `srtm` dataset into the coordinate reference system used in the `zion` object. 

  - Create a new object `srtm2`
  - Visualize the results using the `plot()` function.

* Reproject the `zion` dataset into the coordinate reference system used in the `srtm` object.
  - Create a new object `zion2`

  - Visualize the results (`zion2` together with `srtm2`) using the `plot()` function.
  
## transforming one layer’s CRS to match the other
```{r}
the_crs <- crs(zion, asText = TRUE)

zion_2 <- st_transform(zion, crs = the_crs)

srtm_2 <- projectRaster(srtm, crs = the_crs, method = "ngb")


# Look at the CRS to see if they match
st_crs(zion_2)
st_crs(srtm_2)
```

```{r}
map2 <- plot(srtm_2);plot(zion_2, add = TRUE, col = "transparent")
```

