---
title: "W1 - Interactive Map in Leaflet"
author: "Sofie Thinggaard"
date: "1/2/2022"
output:
  html_document: default
  pdf_document: default
---

Question 1: Describe a problem or question in your field that lends itself to spatial analysis.

-My field: English
-Question: How did the British industrialization 1760-1840 effect Britain's population density? (urbanization)

Question 2: List data layers that you think are necessary to answer your question/solve your problem. Describe examples of two or three of your listed layers and see if you can find them on the internet.

-Data needed: population of Britain and where they lived in the beginning of 1700 and where people lived around 1840
-Two maps: Britain before industrial revolution and a map after
-Color coded to match population density: red= high population density, orange= slightly less, green= lower again
-A similar map: https://www.google.com/search?q=map+urbanization+industrial+revolution&source=lnms&tbm=isch&sa=X&ved=2ahUKEwi4kci-9eD1AhXth4sKHczBCjkQ_AUoAXoECAEQAw&biw=1280&bih=569&dpr=1.5#imgrc=DRH6eBNNNIbRoM 
-Points you can hover over to see the names of the top 5 most crowded cities on both maps
-Mini map for easier interaction

Question 3.	Make a Map (option 1)

## Data folder
```{r}
dir.create("data")
```

## Packages
```{r}
#install.packages("tidyverse")
library(tidyverse)
#install.packages("leaflet")
#install.packages("htmlwidget")
library(leaflet)
library(htmlwidgets)

read_csv("data/RCFeature2018.csv")
```

## 4. Loading in the table of points
```{r}
library(tidyverse)
library(googlesheets4)
library(leaflet)

points <- read_csv("data/RCFeature2018.csv")

glimpse(points)

points_map <- leaflet() %>%
  addTiles() %>%
  setView(lng = 150.300003, lat = -33.700001, zoom = 10) %>% # Blue Mountains coordinates
  addProviderTiles("Esri.WorldPhysical", group = "Physical") %>%
  addProviderTiles("Esri.WorldImagery", group = "Aerial") %>%
  addLayersControl(
    baseGroups = c("Aerial", "Physical"),
    options = layersControlOptions(collapsed = T)) %>%
  addAwesomeMarkers(lng = points$Longitude,
                    lat = points$Latitude,
                    popup = paste("FeatureID:", points$FeatureID, "<br>",
                                  "FeatureType:", points$FeatureType, "<br>",
                                  "Description:", points$Description))

points_map
```
## 5. Adding minimap() and measure()
```{r}
esri <- grep("^Esri", providers, value = TRUE)

for (provider in esri) {
  minimap <- points_map %>% addProviderTiles(provider, group = provider)
}

minimap <- points_map %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
addControl("", position = "topright")

minimap
```

## 6. Differentiating the circlemarkers by size according to the column "accuracy"
```{r}
map_circle <- minimap %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addCircleMarkers(color= "pink", lng = points$Longitude,
                  lat = points$Latitude,
                  radius = points$Accuracy * 2,
                  stroke = FALSE, fillOpacity = 0.5,
                  popup = paste("Feature ID:", points$FeatureID, "<br>",
                                  "Feature Type:", points$FeatureType, "<br>",
                                  "Description:", points$Description)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479")

map_circle
```


## 7. Clustering markers
```{r}
cluster_map <- minimap %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addCircleMarkers(lng = points$Longitude,
                  lat = points$Latitude,
                  radius = points$Accuracy * 2,
                  stroke = FALSE, fillOpacity = 0.5,
                  popup = paste("Feature ID:", points$FeatureID, "<br>",
                                  "Feature Type:", points$FeatureType, "<br>",
                                  "Description:", points$Description),
                  clusterOptions = markerClusterOptions()) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479")

cluster_map
```
Because of the data points are so close to each other, I do not recommend adding the cluster layer
